Figures

### 2021-10-29 manuscript/figures.Rmd
stash figures pdf, closes #3

```{r fig.cap="Realization of a Pareto (A) probability density function and (B) complementary cumulative distribution function.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/pareto_demo-1.pdf")
```

```{r fig.cap="Censored lake area edf (solid line) and cdf estimate (dashed line).", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/predict_censor-1.pdf")
```

@@

```{r fig.cap="Median (black line) and central 95 percent interval estimates of alpha (red lines). Here the 'true' alpha is 0.9.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/bayesian_model-1.pdf")
```

>>>>

```{r fig.cap="Realization of a Pareto (A) probability density function and (B) complementary cumulative distribution function compared against equivalent calculations on the HydroLAKES dataset.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/pareto_demo-1.pdf")
```

```{r fig.cap="Censored lake area edf (solid line) and transformed cdf estimate (dashed line) compared against the HydroLAKES dataset.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/predict_censor-1.pdf")
```

@@

```{r fig.cap="Median (black line) and central 95 percent interval estimates of alpha (red lines). Here the 'true' alpha is 0.9 and is marked with a dashed line.", echo=FALSE, fig.width=1,out.height="4in"}
knitr::include_graphics("../manuscript/figures/bayesian_model-1.pdf")
```
